---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}

activity <- read.csv("~/DataScience/Reproducible/activity.csv")
## Converting date column from factor to date
activity$date <- as.Date(activity$date)

```

## Calculating total number of steps and making a histogram.
## X-axis is total number of steps per day in chunks of 5000 and y-axis is ## the number of measurements i.e. days that fall in each chunk
```{r}
## Using dplyr - loading library
library(dplyr)
## Summing up the number of steps per day
SumStepsDay <- activity %>% 
    group_by(date) %>% 
    summarize(TotalSteps=sum(steps))

## And outputing the histogram
hist(SumStepsDay$TotalSteps, 
     xlab="Total number of steps", 
     ylab="Number of days", 
     main="Total number of steps per day",
     col=8)
```


## What is mean and median of total number of steps taken per day?
## Removing NAs since the result would otherwise be NA
```{r}
mean(SumStepsDay$TotalSteps, na.rm = TRUE)
median(SumStepsDay$TotalSteps, na.rm = TRUE)
```


## What is the average daily activity pattern?
```{r}
```


## Imputing missing values
```{r}
```


## Are there differences in activity patterns between weekdays and weekends?
```{r}
```